FEM Model Analysis

### 2021-04-24 FEM_R/model_analysis_core.Rmd
Removed cancer and heart disease graphs from validation

# Collect the age suffixes into a vector
keep_vars <- c(m_ages, f_ages)
# Now set up the chronic diseases in a list so we can create a bigger list with all of them produced
diseases <- c('hearte', 'hibpe', 'stroke', 'diabe', 'lunge', 'demene', 'asthmae')

@@

pivoted.FEM <- pivot_longer(data = FEM,
                            cols = hearte_m_6064:asthmae_f_100p, 
                            names_to = c('Condition', 'Gender', 'Age_Group'), 
                            names_sep = '_')

@@

# Now need to deal with the fact that ageUK data splits heart issues into 3 different conditions
# extract all heart related conditions for combining
ageUK_heart <- filter(ageUK, Condition == c('Coronary Heart Disease', 'Heart Failure', 'Atrial Fibrillation'))
# Aggregate the values by gender and age group
ageUK_heart <- aggregate(ageUK_heart$value, by = list(ageUK_heart$Gender, ageUK_heart$Age_Group), FUN = sum)
# Rename columns and add condition column back
colnames(ageUK_heart) <- c('Gender', 'Age_Group', 'value')
ageUK_heart$Condition <- 'Heart Problems'

# Now drop the heart problems from original ageUK and replace with aggregate
ageUK <- filter(ageUK, Condition != 'Coronary Heart Disease', Condition != 'Heart Failure', Condition != 'Atrial Fibrillation')
ageUK <- rbind(ageUK, ageUK_heart)

# Rename a few just for completeness
#ageUK$Condition <- gsub("Cancer, recent", "Cancer", ageUK$Condition)
ageUK$Condition <- gsub("COPD", "Lung Disease (COPD)", ageUK$Condition)

@@

# REMOVE CONDITIONS FROM ageUK THAT ARE NOT IN FEM (may change in future)
#ageUK <- filter(ageUK, Condition != c('Asthma', 'Depression', 'Severe Mental Health Condition'))
ageUK <- filter(ageUK, Condition != 'Depression', Condition != 'Severe Mental Health Conditions')
ageUK <- filter(ageUK, Condition != 'Cancer, recent')

@@

# Rename all the conditions to fit ageUK
# NOTE: Lung disease is not a perfect match, as ageUK only contains info on COPD
#       Therefore only validation from this will be that FEM is higher than ageUK
newFEM$Condition <- gsub("hearte", "Heart Problems", newFEM$Condition)
newFEM$Condition <- gsub("hibpe", "Hypertension", newFEM$Condition)
newFEM$Condition <- gsub("stroke", "Stroke", newFEM$Condition)
newFEM$Condition <- gsub("diabe", "Diabetes", newFEM$Condition)
newFEM$Condition <- gsub("lunge", "Lung Disease (COPD)", newFEM$Condition)
#newFEM$Condition <- gsub("cancre", "Cancer", newFEM$Condition)
newFEM$Condition <- gsub("demene", "Dementia", newFEM$Condition)
newFEM$Condition <- gsub("asthmae", "Asthma", newFEM$Condition)

>>>>

# Collect the age suffixes into a vector
keep_vars <- c(m_ages, f_ages)
# Now set up the chronic diseases in a list so we can create a bigger list with all of them produced
diseases <- c('hibpe', 'stroke', 'diabe', 'demene', 'asthmae')

@@

pivoted.FEM <- pivot_longer(data = FEM,
                            cols = hibpe_m_6064:asthmae_f_100p, 
                            names_to = c('Condition', 'Gender', 'Age_Group'), 
                            names_sep = '_')

@@

# Now need to deal with the fact that ageUK data splits heart issues into 3 different conditions
# extract all heart related conditions for combining
#ageUK_heart <- filter(ageUK, Condition == c('Coronary Heart Disease', 'Heart Failure', 'Atrial Fibrillation'))
# Aggregate the values by gender and age group
#ageUK_heart <- aggregate(ageUK_heart$value, by = list(ageUK_heart$Gender, ageUK_heart$Age_Group), FUN = sum)
# Rename columns and add condition column back
#colnames(ageUK_heart) <- c('Gender', 'Age_Group', 'value')
#ageUK_heart$Condition <- 'Heart Problems'

# Now drop the heart problems from original ageUK and replace with aggregate
ageUK <- filter(ageUK, Condition != 'Coronary Heart Disease', Condition != 'Heart Failure', Condition != 'Atrial Fibrillation')
#ageUK <- rbind(ageUK, ageUK_heart)

# Rename a few just for completeness
#ageUK$Condition <- gsub("Cancer, recent", "Cancer", ageUK$Condition)
#ageUK$Condition <- gsub("COPD", "Lung Disease (COPD)", ageUK$Condition)

@@

# REMOVE CONDITIONS FROM ageUK THAT ARE NOT IN FEM (may change in future)
#ageUK <- filter(ageUK, Condition != c('Asthma', 'Depression', 'Severe Mental Health Condition'))
ageUK <- filter(ageUK, Condition != 'Depression', Condition != 'Severe Mental Health Conditions')
ageUK <- filter(ageUK, Condition != 'Cancer, recent', Condition != 'COPD')

@@

# Rename all the conditions to fit ageUK
# NOTE: Lung disease is not a perfect match, as ageUK only contains info on COPD
#       Therefore only validation from this will be that FEM is higher than ageUK
#newFEM$Condition <- gsub("hearte", "Heart Problems", newFEM$Condition)
newFEM$Condition <- gsub("hibpe", "Hypertension", newFEM$Condition)
newFEM$Condition <- gsub("stroke", "Stroke", newFEM$Condition)
newFEM$Condition <- gsub("diabe", "Diabetes", newFEM$Condition)
#newFEM$Condition <- gsub("lunge", "Lung Disease (COPD)", newFEM$Condition)
#newFEM$Condition <- gsub("cancre", "Cancer", newFEM$Condition)
newFEM$Condition <- gsub("demene", "Dementia", newFEM$Condition)
newFEM$Condition <- gsub("asthmae", "Asthma", newFEM$Condition)

#force Make to run this again
